---
title: "final"
author: "zurg"
date: "2025-06-02"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## FINAL HIINTS

tiny_clothes realtions are printed, DO NOT REMEMBER
  - 21 database questions and 29 R questions
    - basic knoweldge or result of running code, filling in the blank
  - dbGetQuery(); various where condition 
  - dbSendQuery()
  - dbFetch()
  - dbSendStatement()
  - dbRowsAffected
  
  - read.csv
  - data.frame
  - matrix
  - array
  - need to know how to generate a sample in R (r.binom)
  - all work on p
  - integrity constraints
  - order by, group by
  - questions on JOINS
  - lists (in R)
  - double bracket notation ([[1]] , [[2,3]])
  - all distributions, binomial, uniform, poisson, exponetial,
     - when to use them and conditions (4 conditions for binomial experiment)
      - p.binom, d.binom
    
  - user defined functions
  - all control strucutres
  - work on descriptive statistics (in R and in general)
  - probability RULES (no bayes)
    - simple calculations 
    
    

## Section Notes

```{r}
dbGetQuery(mdb, 'select ORDER_NO , MAX(QUNAITY) from INVOUICES
           group by OPRER_NO')

```

- WHERE
  - filters for raw data
  - Also for new columns like Price*Quantity
  
- HAVING
  -filters for aggregated data
  - 
  
LOOK FOR MAX() , AVG(), use having, also uses GROUP BY

- ORDER BY
  - defaults to ASCENDING
```{r}

```
  - need to specify DESC (decending)
  
  - breaking ties
    ```{r}
    dbGetQuery
    ```

- Column Position


## JOINS

- Join and ON run together
  - when JOIN cannot find ON > Cartesian Product
  - if you JOIN without ON, you wil always get the cartesian product
  
- INNER JOIN
  - Keeps rows that are similar
- LEFT JOIN
  - Left table needs to find a match on the right.
  - Every row on the left needs to go somehwere
  - if there is no match, <NULL>
- RIGHT JOIN
  - Same thing but from right table
  - arrow has to come from eveyr row
  
  
- to append a data.frame, the data.frame shoudl ahve the same name relations
  - Column names must match
  
  
## View (read-only Table)
   - only gives access to the view table and not entire database
   - used for security. (protect information)
   
   
  


  
